---
title: "Open Source Melt Flow Index"
subtitle: "Fostering Distributed Recycling via Additive Manufacturing"
author: "Fabio CRUZ, Hakim, Joshua Pearce"
institute: "<br/>Université de Lorraine <br/> Michigan Technological University"
date: "Updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      ratio: '16:9'
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)

# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')
```

```{r, include=TRUE, echo=FALSE}
# CSS for the CSS
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio-fonts.css")
htmltools::includeCSS("https://raw.githubusercontent.com/fabbiocrux/presentaciones/gh-pages/Assets-global/css/Fabio.css")
```

# Research Problem

- How to measure the quality of recycled material for distributed recycling based on a *'printability'* notion.

.pull-left[
Printability could be related to:
- $T_g$, $T_m$ , heat capacity $Cp$, viscosity/fluidity, shear stress
How to develop a low cost/replicable equipment for this ?

]

.pull-right[
- 
]



???

---

# Goals

> Design and built an open source rheological device to indicate material’s printability 
comparison with commercial test machines 

- MFI hardware paper to submit to [HardwareX](https://www.journals.elsevier.com/hardwarex) using recycled PLA as the test case; then
- A coupled article on some material science for [Materials and Design](https://www.journals.elsevier.com/materials-and-design/news/reproducibility-co-special-issue-open-hardware-research)
 

---
class: middle center

# Anezka
### Timming: Nov 2019 - April 2020

Main results: 
- first prototype and trials 
- reproducibility of the test
- Calibration procedure


---
## Literature review
- Last update: "`r Sys.Date()`"
- Work document for Anezka research.


---

## Benjamin Hubbard

https://www.appropedia.org/Open_Source_Digitally_Replicable_Lab-Grade_Scales
